An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2023-06-09 poly-embed-journal/reviews/jmlr-response.tex
Small updates to JMLR response

\raf{OLD TEXT}
  We thank the editor and reviewers for their feedback.

We first discuss the changes needed to implement this correction, and then address the changes to address other comments, all of which were minor.\\
\\
Regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

 [See Section 8 for added discussion on $\mathcal{H}$-consistency.]

@@

  \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?}

>>>>

\raf{OLD TEXT}
  We thank the editor and reviewers for their feedback.  
  \jessie{Not sure what else to write here?}

\\
\\
Regards,\\
Jessie Finocchiaro, Rafael Frongillo, and Bo Waggoner

@@

 We thank the reviewer for the references and questions about the connections to $\H$-consistency and calibration. We have added a discussion about possible extensions to Section~\ref{sec:conclusion}. \jessie{TODO?}

@@

  \item \emph{Theorem 33 shows that every possible calibrated link must be produced from construction 2. I am wondering if a similar result holds for construction 1 and embedding?} 
  \raf{TODO}
